The title

### 2023-03-14 doc/manuscript.Rmd
Add PA intensity models

sleep_outcomes_by_PA <- lapply(model_list[sleep_names], function(x){
tab <- format_table(x$table)  
tab
})

names(sleep_outcomes_by_PA) <- gsub("scale_", "", names(sleep_outcomes_by_PA)) |> 
  gsub("\\sby.*", "", x = _ ) |> 
  gsub("_", " ", x = _ ) |> 
  stringr::str_to_sentence()

  papaja::apa_table(sleep_outcomes_by_PA,
                    caption = "Sleep on physical activity volume controlling for SES, gender and BMI",
                    note = note,
                    escape = FALSE)
```

```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on Physical activity volume"}
knitr::include_graphics(here::here("Figures/sleep on pa_volume.jpg"), error = FALSE)

```

>>>>

sleep_outcomes_by_PA_volume <- lapply(model_list[sleep_names], function(x){
tab <- format_table(x$table)  
tab
})

names(sleep_outcomes_by_PA_volume) <- gsub("scale_", "", names(sleep_outcomes_by_PA_volume)) |> 
  gsub("\\sby.*", "", x = _ ) |> 
  gsub("_", " ", x = _ ) |> 
  stringr::str_to_sentence()

  papaja::apa_table(sleep_outcomes_by_PA_volume,
                    caption = "Sleep on physical activity volume controlling for SES, gender and BMI",
                    note = note,
                    escape = FALSE)
```

```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on Physical activity volume"}
knitr::include_graphics(here::here("Figures/sleep on pa_volume.jpg"), error = FALSE)
```

## The effects of physical activty intensity on sleep

```{r sleep-by-intensity}
sleep_names <- c("scale_sleep_duration by scale_pa_intensity", "scale_sleep_efficiency by scale_pa_intensity", 
"scale_sleep_onset by scale_pa_intensity", "scale_sleep_regularity by scale_pa_intensity")

sleep_outcomes_by_PA_intens <- lapply(model_list[sleep_names], function(x){
tab <- format_table(x$table)  
tab
})

names(sleep_outcomes_by_PA_intens) <- gsub("scale_", "", names(sleep_outcomes_by_PA_intens)) |> 
  gsub("\\sby.*", "", x = _ ) |> 
  gsub("_", " ", x = _ ) |> 
  stringr::str_to_sentence()

  papaja::apa_table(sleep_outcomes_by_PA_intens,
                    caption = "Sleep on physical activity intensity controlling for SES, gender and BMI",
                    note = note,
                    escape = FALSE)
```

```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on Physical activity intensity"}
knitr::include_graphics(here::here("Figures/sleep on pa_intensity.jpg"), error = FALSE)
```

### 2023-03-14 doc/manuscript.tex
Fix tag for table 1
Prepare to apply tabulation to other outcomes.
Add PA intensity models

\renewcommand{\arraystretch}{0.8}

@@

\caption{\label{tab:sleep-by-exercise}Sleep on physical activity volume controlling for SES, gender and BMI}

@@

>>>>

\renewcommand{\arraystretch}{0.7}

@@

\caption{\label{tab:sleep-by-volume}Sleep on physical activity volume controlling for SES, gender and BMI}

@@

\hypertarget{the-effects-of-physical-activty-intensity-on-sleep}{%
\subsection{The effects of physical activty intensity on sleep}\label{the-effects-of-physical-activty-intensity-on-sleep}}

\caption{\label{tab:sleep-by-intensity}Sleep on physical activity intensity controlling for SES, gender and BMI}

\begin{tabular}{lllll}
\toprule
Term & \multicolumn{1}{c}{$\beta$ [95\% CI]} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
\midrule
Sleep duration &  &  &  & \\
\ \ \ (Intercept) & -0.41 [-0.97, 0.15] & 0.28 & -1.44 & .243\\
\ \ \ Scale  pa  intensity & 0.09 [0.04, 0.13] & 0.02 & 3.60 & .001\\
\ \ \ Age & 0.00 [0.00, 0.00] & 0.00 & 0.14 & .900\\
\ \ \ Scale  pa  intensity$^2$ & -0.01 [-0.03, 0.02] & 0.01 & -0.61 & .542\\
\ \ \ Scale  pa  intensity:age & 0.00 [0.00, 0.00] & 0.00 & -1.43 & .165\\
\ \ \ Age:scale  pa  intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & -0.52 & .604\\
Sleep efficiency &  &  &  & \\
\ \ \ (Intercept) & -1.00 [-1.41, -0.60] & 0.21 & -4.87 & < .001\\
\ \ \ Scale  pa  intensity & 0.13 [0.04, 0.22] & 0.05 & 2.75 & .062\\
\ \ \ Age & 0.01 [0.01, 0.02] & 0.00 & 10.22 & .002\\
\ \ \ Scale  pa  intensity$^2$ & 0.01 [-0.02, 0.04] & 0.01 & 0.78 & .436\\
\ \ \ Scale  pa  intensity:age & 0.00 [0.00, 0.00] & 0.00 & -1.95 & .113\\
\ \ \ Age:scale  pa  intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & -1.71 & .088\\
Sleep onset &  &  &  & \\
\ \ \ (Intercept) & -0.96 [-1.49, -0.44] & 0.27 & -3.60 & .065\\
\ \ \ Scale  pa  intensity & -0.04 [-0.07, -0.01] & 0.02 & -2.46 & .015\\
\ \ \ Age & 0.02 [0.02, 0.02] & 0.00 & 9.64 & .007\\
\ \ \ Scale  pa  intensity$^2$ & 0.00 [-0.02, 0.02] & 0.01 & 0.38 & .703\\
\ \ \ Scale  pa  intensity:age & 0.00 [0.00, 0.00] & 0.00 & -0.37 & .714\\
\ \ \ Age:scale  pa  intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & 1.51 & .143\\
Sleep regularity &  &  &  & \\
\ \ \ (Intercept) & -0.24 [-0.47, -0.02] & 0.11 & -2.09 & .123\\
\ \ \ Scale  pa  intensity & 0.30 [0.25, 0.34] & 0.02 & 13.30 & < .001\\
\ \ \ Age & 0.01 [0.01, 0.01] & 0.00 & 6.88 & .004\\
\ \ \ Scale  pa  intensity$^2$ & -0.05 [-0.07, -0.02] & 0.01 & -3.48 & .001\\
\ \ \ Scale  pa  intensity:age & 0.00 [0.00, 0.00] & 0.00 & -6.20 & < .001\\
\ \ \ Age:scale  pa  intensity$^2$ & 0.00 [0.00, 0.00] & 0.00 & 0.33 & .743\\
\bottomrule
\addlinespace
\end{tabular}

\begin{figure}
\includegraphics[width=7.08in]{../Figures/sleep on pa_intensity} \caption{Sleep metrics on Physical activity intensity}\label{fig:sleep-by-intensity-fig}
\end{figure}
